\emph{Light Exposure Behavior Assessment (LEBA)}: Develop of a novel instrument to capture light exposure-related behaviours

### 2021-09-04 manuscript.Rmd

```{r setup, include = FALSE}
library(papaja) # devtools::install_github("crsh/papaja")
library(readr)
library(readxl)
library(lavaan)
library(semPlot)
library(semTools)
library(MOTE)
library(psych)
library(dlookr)
library(tidyverse)
library(qgraph)
library(kableExtra)
library(paran) # Parallel analysis
library(EFA.MRFA) # Hull method
library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
library(DiagrammeRsvg) #For DiagrammeR
library(rsvg) #For DiagrammeR
library(correlation)
library(ggcorrplot)
r_refs("references.bib")
```

@@

@@

```{r Normality assumption EFA, include=FALSE}
LB <- read_excel("recoded not reversed_EFA.xlsx")
LB$X1 <- NULL
#KMO test
KMO <- KMO(LB)

# Test of correlation matrix
bartlet <- cortest.bartlett(LB, n =428)

# Univariante normality
normality <- normality(LB) 
normalityprefix <- apa(normality$statistic, 2,T)
normalitysufix <- "*"
normality.names <- paste(normalityprefix,normalitysufix, sep = "" )

# Multivariate Normality
mardia <- mardia(LB, na.rm = T, plot =F)

# Descriptives
Descriptives <- psych::describe(LB)
alpha <- psych::alpha(LB)
Item.total <- alpha$item.stats

@@

#Polychoric Correlation matrix
LB.factor <- sapply(LB, as.factor)
correlations <- polychoric(LB.factor, correct = 0)
upper <- correlations$rho[upper.tri(correlations$rho, diag = F)]

@@

BigR = sum(correlations$rho >= abs(.30) & correlations$rho < abs(1.0), na.rm =T)/2 
totR = length(LB)*(length(LB)-1)/2
cor.per <- print (BigR/totR)*100

# Item analysis
Item_analysis <- psych::alpha(LB)
Item_analysis$item.stats$r.cor
R.cor.sum <- summary(Item_analysis$item.stats$r.cor)
low.r.corec <- abs(R.cor.sum[1])  #minimum item total correlation
high.r.corec <- R.cor.sum[6]     # maximum item total correlation
```

@@

#correlations <- polychoric(LB.factor, correct = 0)

@@

# HULL
hullEFA(LB,extr = "ULS", index_hull = "CAF", display = TRUE, graph = TRUE,
        details = TRUE)

@@

reduced.model.5F.1 <- dplyr::select(LB ,
                                    - c(item20,item17,item3, item15,item40, item4,item11, item39,
                                        item18, item45, item29, item25, item8, item46 ))

@@

fa.5F.2 <- fa(r=correlations.red.5F.1$rho, nfactors = 5, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)
BB <- print(fa.5F.2, cut = .3, digits = 3, sort = TRUE)

reduced.model.5F.2 <- dplyr::select(LB,- c(item20,item17,item3, item15,item40, item4,item11, item39,
                                           item18, item45, item29, item25, item8, item46,
                                           item33, item12,item31, item37,
                                           item22, item38, item6, item48))
correlations.red.5F.2 <- polychoric(reduced.model.5F.2,correct = 0)

fa.5F.3 <- fa(r=correlations.red.5F.2$rho, nfactors = 5, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)

@@

reduced.model.5F.3 <- dplyr::select(LB,- c(item20,item17,item3, item15,item40, item4,item11, item39,
                                           item18, item45, item29, item25, item8, item46,
                                           item33, item12,item31, item37,
                                           item22, item38, item6, item48, item9, item42,
                                           item23))
correlations.red.5F.3 <- polychoric(reduced.model.5F.3,correct = 0)

fa.5F.4 <- fa(r=correlations.red.5F.3$rho, nfactors = 5, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)

DD <- print(fa.5F.4, cut = .3, digits = 3, sort = TRUE)

@@

# node definitions with substituted label text
node [fontname = Helvetica, shape = circle,  margin = 0.5, width = 3.5, height = .5,
fixedsize = true, fontsize = 35]
F1 [label = 'Blue 
Filter']
F2 [label = 'Outdoor']
F3 [label = 'Sleep
Environment']
F4 [label = 'Cell Phone']
F5 [label = 'Awareness']
node [fontname = Helvetica, shape = box]
b [label = 'item43']
c [label = 'item26']
d [label = 'item32']
e [label = 'item10']
f [label = 'item47']
g [label = 'item36']
h [label = 'item44']
i [label = 'item35']
j [label = 'item13']
k [label = 'item14']
l [label = 'item41']
m [label = 'item7']
n [label = 'item27']
o [label = 'item21']
p [label = 'item34']
q [label = 'item19']
r [label = 'item2']
s [label = 'item5']
t [label = 'item24']
u [label = 'item30']
v [label = 'item1']
w [label = 'item16']
x [label = 'item28']

{rank = same; F1 F2 F3 F4 F5}
# edge definitions with the node IDs
edge [fontname = Helvetica, fontsize = 35]
F1 -> b[label = '0.99']
F1-> c [label = '0.93']
F1-> d [label = '0.80']
F2 -> e [label = '0.82']
F2 -> f[label = '0.82']
F2 -> g [label = '0.63']
F2 -> h[ label = '-0.47', color =red]
F2 -> i [label = '0.46']
F2 -> j [label = '0.34']
F3 -> k [label = '0.89']
F3 -> l [label = '0.70']
F3 -> m [label = '0.66']
F3 -> n [label = '0.38']
F3 -> o [label = '-0.34', color =red]
F4 -> p [label = '0.84']
F4 -> q [label = '0.80']
F4 -> r [label = '0.69']
F5 -> s [label = '0.69']
F5 -> t [label = '0.54']
F5 -> u [label = '0.52']
F5 -> v [label = '0.35']
F5 -> w [label = '0.31']
F5 -> x [label = '0.31']

}
")

@@

```{r Cronbach alpha for 5 fators, message=TRUE, warning=FALSE, include=FALSE}
Five.F1 <- dplyr::select(LB, item43, item26, item32)
Five.F2 <- dplyr::select(LB, item10, item47, item36, item44, item35, item13) 
Five.F3 <-  dplyr::select(LB, item14, item41,item7, item27, item21)
Five.F4 <-  dplyr::select(LB, item19,item34,item2)
Five.F5 <- dplyr::select(LB, item5, item24, item30, item1, item16, item28)

Five.F1.alpha <- psych::alpha(Five.F1, check.keys = T) 
Five.F2.alpha <- psych::alpha(Five.F2, check.keys = T)
Five.F3.alpha <- psych::alpha(Five.F3, check.keys = T)
Five.F4.alpha <- psych::alpha(Five.F4, check.keys = T) 
Five.F5.alpha <- psych::alpha(Five.F5, check.keys = T) 
```

@@

reduced.model.5F.min.1 <- dplyr::select(LB ,
                                    - c(item20,item17,item3, item15,item40, item4,item11, item39,
                                        item18, item45, item29, item25, item8, item46 ))

@@

fa.5F.min.2 <- fa(r=correlations.red.5F.min.1$rho, nfactors = 5, fm= "minres",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)
FF <- print(fa.5F.min.2, cut = .3, digits = 3, sort = TRUE)

reduced.model.5F.min.2 <- dplyr::select(LB,- c(item20,item17,item3, item15,item40, item4,item11, item39,
                                           item18, item45, item29, item25, item8, item46,
                                           item33, item12,item31, item37,
                                           item22, item38, item6, item48))

@@

GG <- print(fa.5F.min.3, cut = .3, digits = 3, sort = TRUE)

reduced.model.5F.min.3 <- dplyr::select(LB,- c(item20,item17,item3, item15,item40, item4,item11, item39,
                                               item18, item45, item29, item25, item8, item46,
                                               item33, item12,item31, item37,
                                               item22, item38, item6, item48,
                                               item9, item42, item23))
correlations.red.5F.min.3 <- polychoric(reduced.model.5F.min.3,correct = 0)

fa.5F.min.4 <- fa(r=correlations.red.5F.min.3$rho, nfactors = 5, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)

HH <- print(fa.5F.min.4, cut = .3, digits = 3, sort = TRUE)

@@

#LB.factor <- sapply(LB, as.factor)
#correlations <- polychoric(LB.factor, correct = 0)

fa.6F.1 <- fa(r=correlations$rho, nfactors = 6, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)
II <- print(fa.6F.1, cut = .3, digits = 3, sort = TRUE)

reduced.model.6F.1 <- dplyr::select(LB ,
                                    -c(item15, item17, item40, item4, item3, item46, item8,item29, item25 ))

@@

fa.6F.2 <- fa(r=correlations.red.6F.1$rho, nfactors = 6, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)
JJ <- print(fa.6F.2, cut = .3, digits = 3, sort = TRUE)

reduced.model.6F.2 <- dplyr::select(LB,-c(item15, item17, item40, item4, item3, item46, item8,item29, item25, item9, item33, item48, item16, item6 ))

@@

fa.6F.3 <- fa(r=correlations.red.6F.2$rho, nfactors = 6, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)

@@

reduced.model.6F.3 <- dplyr::select(LB,- -c(item15, item17, item40, item4, item3, item46, item8,item29, item25, item9, item33, item48, item16, item6, item11, item23, item18, item39))

correlations.red.6F.3 <- polychoric(reduced.model.6F.3,correct = 0)

fa.6F.4 <- fa(r=correlations.red.6F.3$rho, nfactors = 6, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428, max.iter = 500)

LL <- print(fa.6F.4, cut = .3, digits = 3, sort = TRUE)

# Residuals
residual.6F =residuals(fa.6F.4 , diag = FALSE, na.rm =T)
#Count of numbers of residuals>.05
BigRRR= sum(residual.6F>abs(.05), na.rm =T)
print(BigRRR)

#Total number of off diagonal elements in the data matrix
totRRR = length(reduced.model.6F.3)*(length(reduced.model.6F.3)-1)/2

@@

```{r factordetails, include=FALSE}
#Preparing the EFA table
factor.des = matrix(, nrow = 25, ncol = 6)
as.table(factor.des)
rownames(factor.des) <- c("item43", "item26",  "item32",   
                          "item10",  "item47",  "item36", "item44",  "item35",  "item13", 
                          "item14", "item41",  "item7","item27","item21",
                          "item34", "item19", "item2",
                          "item5", "item24", "item30", "item1", "item16", "item28", "internal Consistency","% of variance")

@@

factor.des[,1] <- c(.99, .93, .80, "-","-","-","-","-","-","-","-","-","-","-","-",
                    "-","-","-","-","-","-","-","-",apa(Five.F1.alpha$total[,1],2,F), 11)

factor.des[,2] <- c("-", "-", "-", .82,.82,.63,-.47,.46,.34,"-","-","-","-","-","-",
                    "-","-","-","-","-","-","-","-",apa(Five.F2.alpha$total[,1],2,F), 10)

factor.des[,3] <- c("-", "-", "-", "-","-","-","-","-","-",.89,.70,.66,.38,-.34,"-",
                    "-","-","-","-","-","-","-","-", apa(Five.F3.alpha$total[,1],2,F),9)

factor.des[,4] <- c("-", "-", "-", "-","-","-","-","-","-","-","-","-","-","-",.84,
                    .80,.67,"-","-","-","-","-","-",apa(Five.F4.alpha$total[,1],2,F), 9)

factor.des[,5] <- c("-", "-", "-", "-","-","-","-","-","-","-","-","-","-","-","-","-","-"
                    ,.69,.54,.52,.35,.31,.31,apa(Five.F5.alpha$total[,1],2,F), 6)

factor.des[,6] <- c (.99, .90,.67,.68,.70,.45,.24,.24,.13,.81,.60,.45,.21,.12,.74,.64,.54,
                     .51,.33,.29,.13,.21,.10, "-", "-")

#Commonality
Fac.5 <- fa.5F.4
min.com <- min(Fac.5$communality)
max.com <- max(Fac.5$communality)

@@

# Residuals
residual.5F =residuals(fa.5F.4, diag = FALSE, na.rm =T)
#Count of numbers of residuals>.05
BigRR= sum(residual.5F>abs(.05), na.rm =T)
print(BigRR)

#Total number of off diagonal elements in the data matrix
totRR = length(reduced.model.5F.3)*(length(reduced.model.5F.3)-1)/2

@@

The initial five-factor solution with all 48 items showed presence of cross-loading items (item 42, 16, & 1) and poor factor loading (<.30) items (item 20, 3 ,15, 17, 40, 4, 11, 39, 18, 45, 29, 25, 8 , & 46). At first, we discarded the items with poor factor-loading and ran another EFA on the remaining 34 items. This iteration of EFA also appeared as a misfit with items with poor factor-loading (Item 12, 22, 38, 6) and cross-loading (items 23, 31, 37, 48) . Another two rounds of EFA were conducted with gradually identifying problematic items and discarding them from the model. Finally, a five-factor EFA solution with 23 items was accepted with low RMSR = 0.04 [@brownConfirmatoryFactorAnalysis2015], all factor-loading higher than .30 and no cross-loading greater than .30. We confirmed this five-factor latent structure using varimax rotation with a minimum residual extraction method (see the supplementary). Table\@ref(tab:TabEFA5) displays the factor-loading (structural coefficients) and communality of the items. The absolute value of the factor-loading ranged from `r apa(min.loadings,2,F)` to `r apa(max.loadings, 2, F)` indicating strong coefficients. The commonalities ranged between `r apa(min.com,2,F)` to `r apa(max.com, 2, F)`. However, the histogram of the absolute values of non-redundant residual-correlations (Fig\@ref(fig:Residuals) showed `r apa(sumR,2, T)`% correlations greater than the absolute value of .05, indicating under-factoring. [@desjardinsHandbookEducationalMeasurement2018a]. Subsequently, we fitted a six-factor solution. However, a factor emerged with only two salient variable loading in the six-factor solution, thus disqualifying the six-factor solution.

>>>>

```{r setup, include = FALSE}
library(papaja) # devtools::install_github("crsh/papaja")
library(lavaan)
library(semPlot)
library(semTools)
library(MOTE)
library(psych)
library(dlookr)
library(tidyverse)
library(qgraph)
library(kableExtra)
library(paran) # Parallel analysis
library(EFA.MRFA) # Hull method
library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
library(DiagrammeRsvg) #For DiagrammeR
library(rsvg) #For DiagrammeR
library(correlation)
library(ggcorrplot)
library(car) #Reversecoding
library(Hmisc)
r_refs("references.bib")
```

@@

```{r include=FALSE}
data <- readRDS("leba_2021-09-03.rds")
sem.data <- data[, 6:53] #EFA & CFA data
sem.data[ sem.data == 0] <- 1 #Merged "0"s and "1"s into "1"s

#renaming the column-header
prefix <- "item"
sufix <- c(1:48)
colnam <- paste(prefix,sufix, sep = "" )
colnames(sem.data) <- colnam

#Separating the EFA and CFA sample
EFA.data <- sem.data[1:428, ]
CFA.data <- sem.data[429:690,]

@@

```{r Normality assumption EFA, include=FALSE}

#KMO test
KMO <- KMO(EFA.data)

# Test of correlation matrix
bartlet <- cortest.bartlett(EFA.data, n =428)

# Univariate normality

#for ( i in 1:length (EFA.data)){numeric <- is.numeric(i) print(numeric)}

shapiro.test(EFA.data$item1)

n1 <- shapiro.test(EFA.data$item1)
n2 <- shapiro.test(EFA.data$item2)
n3 <- shapiro.test(EFA.data$item3)
n4 <- shapiro.test(EFA.data$item4)
n5 <- shapiro.test(EFA.data$item5)
n6 <- shapiro.test(EFA.data$item6)
n7 <- shapiro.test(EFA.data$item7)
n8 <- shapiro.test(EFA.data$item8)
n9 <- shapiro.test(EFA.data$item9)
n10 <- shapiro.test(EFA.data$item10)
n11 <- shapiro.test(EFA.data$item11)
n12 <- shapiro.test(EFA.data$item12)
n13 <- shapiro.test(EFA.data$item13)
n14 <- shapiro.test(EFA.data$item14)
n15 <- shapiro.test(EFA.data$item15)
n16 <- shapiro.test(EFA.data$item16)
n17 <- shapiro.test(EFA.data$item17)
n18 <- shapiro.test(EFA.data$item18)
n19 <- shapiro.test(EFA.data$item19)
n20 <- shapiro.test(EFA.data$item20)
n21 <- shapiro.test(EFA.data$item21)
n22 <- shapiro.test(EFA.data$item22)
n23 <- shapiro.test(EFA.data$item23)
n24 <- shapiro.test(EFA.data$item24)
n25 <- shapiro.test(EFA.data$item25)
n26 <- shapiro.test(EFA.data$item26)
n27 <- shapiro.test(EFA.data$item27)
n28 <- shapiro.test(EFA.data$item28)
n29 <- shapiro.test(EFA.data$item29)
n30 <- shapiro.test(EFA.data$item30)
n31 <- shapiro.test(EFA.data$item31)
n32 <- shapiro.test(EFA.data$item32)
n33 <- shapiro.test(EFA.data$item33)
n34 <- shapiro.test(EFA.data$item34)
n35 <- shapiro.test(EFA.data$item35)
n36 <- shapiro.test(EFA.data$item36)
n37 <- shapiro.test(EFA.data$item37)
n38 <- shapiro.test(EFA.data$item38)
n39 <- shapiro.test(EFA.data$item39)
n40 <- shapiro.test(EFA.data$item40)
n41 <- shapiro.test(EFA.data$item41)
n42 <- shapiro.test(EFA.data$item42)
n43 <- shapiro.test(EFA.data$item43)
n44 <- shapiro.test(EFA.data$item44)
n45 <- shapiro.test(EFA.data$item45)
n46 <- shapiro.test(EFA.data$item46)
n47 <- shapiro.test(EFA.data$item47)
n48 <- shapiro.test(EFA.data$item48)

normality.tab = matrix(, nrow = 48, ncol = 2)
as.table(normality.tab)

rownameprefix <- "Item"
rownamesufix <- seq(1:48)
my.item.names <- paste(rownameprefix,rownamesufix, sep = "" )

rownames(normality.tab) <- my.item.names
colnames(normality.tab) <- c("statistic", "p")

normality.tab[,1] <- c(apa((n1$statistic),2,T),
                       apa((n1$statistic),2,T),
                       apa((n3$statistic),2,T),
                       apa((n4$statistic),2,T),
                       apa((n5$statistic),2,T),
                       apa((n6$statistic),2,T),
                       apa((n7$statistic),2,T),
                       apa((n8$statistic),2,T),
                       apa((n9$statistic),2,T),
                       apa((n10$statistic),2,T),
                       apa((n11$statistic),2,T),
                       apa((n12$statistic),2,T),
                       apa((n13$statistic),2,T),
                       apa((n14$statistic),2,T),
                       apa((n14$statistic),2,T),
                       apa((n16$statistic),2,T),
                       apa((n17$statistic),2,T),
                       apa((n18$statistic),2,T),
                       apa((n19$statistic),2,T),
                       apa((n20$statistic),2,T),
                       apa((n21$statistic),2,T),
                       apa((n22$statistic),2,T),
                       apa((n23$statistic),2,T),
                       apa((n24$statistic),2,T),
                       apa((n25$statistic),2,T),
                       apa((n26$statistic),2,T),
                       apa((n27$statistic),2,T),
                       apa((n28$statistic),2,T),
                       apa((n29$statistic),2,T),
                       apa((n30$statistic),2,T),
                       apa((n31$statistic),2,T),
                       apa((n32$statistic),2,T),
                       apa((n33$statistic),2,T),
                       apa((n34$statistic),2,T),
                       apa((n35$statistic),2,T),
                       apa((n36$statistic),2,T),
                       apa((n37$statistic),2,T),
                       apa((n38$statistic),2,T),
                       apa((n39$statistic),2,T),
                       apa((n40$statistic),2,T),
                       apa((n41$statistic),2,T),
                       apa((n42$statistic),2,T),
                       apa((n43$statistic),2,T),
                       apa((n44$statistic),2,T),
                       apa((n45$statistic),2,T),
                       apa((n46$statistic),2,T),
                       apa((n47$statistic),2,T),
                       apa((n48$statistic),2,T))

normality.tab[,2] <- c(apa((n1$p.value),2,T),
                       apa((n1$p.value),2,T),
                       apa((n3$p.value),2,T),
                       apa((n4$p.value),2,T),
                       apa((n5$p.value),2,T),
                       apa((n6$p.value),2,T),
                       apa((n7$p.value),2,T),
                       apa((n8$p.value),2,T),
                       apa((n9$p.value),2,T),
                       apa((n10$p.value),2,T),
                       apa((n11$p.value),2,T),
                       apa((n12$p.value),2,T),
                       apa((n13$p.value),2,T),
                       apa((n14$p.value),2,T),
                       apa((n14$p.value),2,T),
                       apa((n16$p.value),2,T),
                       apa((n17$p.value),2,T),
                       apa((n18$p.value),2,T),
                       apa((n19$p.value),2,T),
                       apa((n20$p.value),2,T),
                       apa((n21$p.value),2,T),
                       apa((n22$p.value),2,T),
                       apa((n23$p.value),2,T),
                       apa((n24$p.value),2,T),
                       apa((n25$p.value),2,T),
                       apa((n26$p.value),2,T),
                       apa((n27$p.value),2,T),
                       apa((n28$p.value),2,T),
                       apa((n29$p.value),2,T),
                       apa((n30$p.value),2,T),
                       apa((n31$p.value),2,T),
                       apa((n32$p.value),2,T),
                       apa((n33$p.value),2,T),
                       apa((n34$p.value),2,T),
                       apa((n35$p.value),2,T),
                       apa((n36$p.value),2,T),
                       apa((n37$p.value),2,T),
                       apa((n38$p.value),2,T),
                       apa((n39$p.value),2,T),
                       apa((n40$p.value),2,T),
                       apa((n41$p.value),2,T),
                       apa((n42$p.value),2,T),
                       apa((n43$p.value),2,T),
                       apa((n44$p.value),2,T),
                       apa((n45$p.value),2,T),
                       apa((n46$p.value),2,T),
                       apa((n47$p.value),2,T),
                       apa((n48$p.value),2,T))

normalityprefix <- normality.tab[,1]
normalitysufix <- "*"
normality.names <- paste(normalityprefix,normalitysufix, sep = "" )

# Multivariate Normality
mardia <- mardia(EFA.data, na.rm = T, plot =F)

# Descriptives
Descriptives <- psych::describe(EFA.data)
alpha <- psych::alpha(EFA.data)
Item.total <- alpha$item.stats

@@

#Polychoric Correlation matrix

correlations <- polychoric(EFA.data, correct = 0)
upper <- correlations$rho[upper.tri(correlations$rho, diag = F)]

@@

BigR = sum(correlations$rho >= abs(.30) & correlations$rho < abs(1.0), na.rm =T)/2 
totR = length(EFA.data)*(length(EFA.data)-1)/2
cor.per <- print (BigR/totR)*100

# Item analysis
Item_analysis <- psych::alpha(EFA.data)
Item_analysis$item.stats$r.cor
R.cor.sum <- summary(Item_analysis$item.stats$r.cor)
low.r.corec <- abs(R.cor.sum[1])  #minimum item total correlation
high.r.corec <- R.cor.sum[6]     # maximum item total correlation
```

@@

#correlations <- polychoric(EFA.factor, correct = 0)

@@

# HULL
hullEFA(EFA.data,extr = "ULS", index_hull = "CAF", display = TRUE, graph = TRUE,
        details = TRUE)

#MAP
psych::VSS(EFA.data, rotate = "varimax", fm = 'minres', n.obs =428 )

@@

reduced.model.5F.1 <- dplyr::select(EFA.data ,
                                    -c( item20, item19, item5, item31, item44, item24, item43, item39, item22, item2, item18, item48, item42, item29, item6, item15, item23, item28, item14))

@@

fa.5F.2 <- fa(r=correlations.red.5F.1$rho, nfactors = 5, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)

BB <- print(fa.5F.2, cut = .3, digits = 3, sort = TRUE)

reduced.model.5F.2 <- dplyr::select(EFA.data, -c( item20, item19, item5, item31, item44, item24, item43, item39, item22, item2, item18, item48, item42, item29, item6, item15, item23, item28, item14, item34, item47, item21, item13))

correlations.red.5F.2 <- polychoric(reduced.model.5F.2,correct = 0)

fa.5F.3 <- fa(r=correlations.red.5F.2$rho, nfactors = 5, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428,max.iter = 500 )

@@

var1 <- CC$Vaccounted[2,1]*100
var2 <- CC$Vaccounted[2,2]*100
var3 <- CC$Vaccounted[2,3]*100
var4 <- CC$Vaccounted[2,4]*100
var5 <- CC$Vaccounted[2,5]*100
```

@@

# node definitions with substituted label text
node [fontname = Helvetica, shape = circle,  margin = 0.5, width = 3.5, height = .5,
fixedsize = true, fontsize = 35]
F1 [label = 'F1']
F2 [label = 'F2']
F3 [label = 'F3']
F4 [label = 'F4']
F5 [label = 'F5']
node [fontname = Helvetica, shape = box]
b [label = 'item16']
c [label = 'item36']
d [label = 'item17']
e [label = 'item11']
f [label = 'item10']
g [label = 'item12']
h [label = 'item7']
i [label = 'item8']
j [label = 'item9']
k [label = 'item27']
l [label = 'item3']
m [label = 'item40']
n [label = 'item30']
o [label = 'item41']
p [label = 'item33']
q [label = 'item32']
r [label = 'item35']
s [label = 'item37']
t [label = 'item38']
u [label = 'item46']
v [label = 'item45']
w [label = 'item25']
x [label = 'item4']
y [label = 'item1']
z [label = 'item26']

{rank = same; F1 F2 F3 F4 F5}
# edge definitions with the node IDs
edge [fontname = Helvetica, fontsize = 35]
F1 -> b[label = '0.99']
F1-> c [label = '0.93']
F1-> d [label = '0.80']
F2 -> e [label = '0.79']
F2 -> f[label = '0.76']
F2 -> g [label = '0.65']
F2 -> h[ label = '0.50']
F2 -> i [label = '-.49',color =red]
F2 -> j [label = '0.32']
F3 -> k [label = '0.80']
F3 -> l [label = '0.80']
F3 -> m [label = '0.65']
F3 -> n [label = '0.49']
F3 -> o [label = '36']
F4 -> p [label = '0.74']
F4 -> q [label = '0.73']
F4 -> r [label = '0.66']
F4 -> s [label = '-0.39', color =red]
F4 -> t [label = '0.39']
F5 -> u [label = '0.60']
F5 -> v [label = '0.59']
F5 -> w [label = '0.41']
F5 -> x [label = '0.41']
F5 -> y [label = '0.40']
F5 -> z [label = '0.35']
}
")

@@

```{r Cronbach alpha for 5 fators, message=TRUE, warning=FALSE, include=FALSE}
Five.F1 <- dplyr::select(EFA.data, item16, item36, item17)
Five.F2 <- dplyr::select(EFA.data, item11, item10, item12, item7, item8, item9) 
Five.F3 <-  dplyr::select(EFA.data, item27, item3,item40, item30, item41)
Five.F4 <-  dplyr::select(EFA.data, item33,item32,item35, item37, item38)
Five.F5 <- dplyr::select(EFA.data, item46, item45, item25, item4, item1, item26)

Five.F1.alpha <- psych::alpha(Five.F1, check.keys = T) 
Five.F2.alpha <- psych::alpha(Five.F2, check.keys = T)
Five.F3.alpha <- psych::alpha(Five.F3, check.keys = T)
Five.F4.alpha <- psych::alpha(Five.F4, check.keys = T) 
Five.F5.alpha <- psych::alpha(Five.F5, check.keys = T)

F1.alpha <- Five.F1.alpha$total$raw_alpha
F2.alpha <- Five.F2.alpha$total$raw_alpha
F3.alpha <- Five.F3.alpha$total$raw_alpha
F4.alpha <- Five.F4.alpha$total$raw_alpha
F5.alpha <- Five.F5.alpha$total$raw_alpha
```

@@

reduced.model.5F.min.1 <- dplyr::select(EFA.data ,
                                    -c( item20, item19, item5, item31, item44, item24, item43, item39, item22, item2, item18, item48, item42, item29, item6, item15, item23, item28, item14))

@@

fa.5F.min.2 <- fa(r=correlations.red.5F.min.1$rho, nfactors = 5, fm= "minres",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)

FF <- print(fa.5F.min.2, cut = .3, digits = 3, sort = TRUE)

reduced.model.5F.min.2 <- dplyr::select(EFA.data, -c( item20, item19, item5, item31, item44, item24, item43, item39, item22, item2, item18, item48, item42, item29, item6, item15, item23, item28, item14, item34, item47, item21, item13))

@@

GG <- print(fa.5F.min.3, cut = .3, digits = 3, sort = TRUE)
```

@@

#EFA.factor <- sapply(EFA.data, as.factor)
#correlations <- polychoric(EFA.factor, correct = 0)

fa.6F.1 <- fa(r=correlations$rho, nfactors = 6, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)

II <- print(fa.6F.1, cut = .3, digits = 3, sort = TRUE)

reduced.model.6F.1 <- dplyr::select(EFA.data ,
                                    -c(item34, item44, item48, item43, item39, item22, item2, item20, item21, item24,item30, item14, item28, item6, item15, item23))

@@

fa.6F.2 <- fa(r=correlations.red.6F.1$rho, nfactors = 6, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428)

JJ <- print(fa.6F.2, cut = .3, digits = 3, sort = TRUE)

reduced.model.6F.2 <- dplyr::select(EFA.data, -c(item34, item44, item48, item43, item39, item22, item2, item20, item21, item24,item30, item14, item28, item6, item15, item23, item18, item42, item47, item41))

@@

fa.6F.3 <- fa(r=correlations.red.6F.2$rho, nfactors = 6, fm= "pa",rotate ="varimax",
              residuals = TRUE, SMC = TRUE, n.obs =428, max.iter = 500)

@@

# Residuals
residual.6F =residuals(fa.6F.3 , diag = FALSE, na.rm =T)
#Count of numbers of residuals>.05
BigRRR= sum(residual.6F>abs(.05), na.rm =T)
print(BigRRR)

#Total number of off diagonal elements in the data matrix
totRRR = length(reduced.model.6F.2)*(length(reduced.model.6F.2)-1)/2

@@

```{r factordetails, include=FALSE}
#Preparing the EFA table
factor.des = matrix(, nrow = 27, ncol = 6)
as.table(factor.des)
rownames(factor.des) <- c("item16", "item36",  "item17",   
                          "item11",  "item10",  "item12", "item7",  "item8",  "item9", 
                          "item27", "item3",  "item40","item30","item41",
                          "item33", "item32", "item35","item37", "item38",
                          "item46", "item45", "item25", "item4", "item1", "item26", "internal Consistency","% of variance")

@@

factor.des[,1] <- c(.99, .94, .80, "-","-","-","-","-","-","-","-","-","-","-","-",
                    "-","-","-","-","-","-","-","-","-","-",apa(Five.F1.alpha$total[,1],2,F), apa(var1,2,F))

factor.des[,2] <- c("-", "-", "-", .80,.76,.65,.50,-.50,.32,"-","-","-","-","-","-",
                    "-","-","-","-","-","-","-","-","-","-",apa(Five.F2.alpha$total[,1],2,F), apa(var2,2,F))

factor.des[,3] <- c("-", "-", "-", "-","-","-","-","-","-",.80,.80,.65,.45,-.36,"-",
                    "-","-","-","-","-","-","-","-","-","-", apa(Five.F3.alpha$total[,1],2,F),apa(var3,2,F))

factor.des[,4] <- c("-", "-", "-", "-","-","-","-","-","-","-","-","-","-","-",.74,
                    .73,.66,-.39,.36,"-","-","-","-","-","-",apa(Five.F4.alpha$total[,1],2,F), apa(var4,2,F))

factor.des[,5] <- c("-", "-", "-", "-","-","-","-","-","-","-","-","-","-","-","-","-","-","-","-",
                    .60,.59,.41,.41,.40,.39,apa(Five.F5.alpha$total[,1],2,F), apa(var5,2,F))

factor.des[,6] <- c (.99, .90,.66,.64, .59, .47, .27, .25, .11, .66, .68, .46, .35, .33, .56, .62, .45, .17, .18, .42, .37, .19, .22, .17, .17, "-", "-")

#Commonality
Fac.5 <- fa.5F.3
min.com <- min(Fac.5$communality)
max.com <- max(Fac.5$communality)

@@

# Residuals
residual.5F =residuals(fa.5F.3, diag = FALSE, na.rm =T)
#Count of numbers of residuals>.05
BigRR= sum(residual.5F>abs(.05), na.rm =T)
print(BigRR)

#Total number of off diagonal elements in the data matrix
totRR = length(reduced.model.5F.2)*(length(reduced.model.5F.2)-1)/2

@@

Three rounds of EFA starting with all 48 items were conducted and problematic items were gradually discarded (cross-loading items and poor factor loading (<.30) items). Finally, a five-factor EFA solution with 25 items was accepted with low RMSR = 0.08 [@brownConfirmatoryFactorAnalysis2015], all factor-loading higher than .30 and no cross-loading greater than .30. We confirmed this five-factor latent structure using varimax rotation with a minimum residual extraction method (see the supplementary). Table\@ref(tab:TabEFA5) displays the factor-loading (structural coefficients) and communality of the items. The absolute value of the factor-loading ranged from `r apa(min.loadings,2,F)` to `r apa(max.loadings, 2, F)` indicating strong coefficients. The commonalities ranged between `r apa(min.com,2,F)` to `r apa(max.com, 2, F)`. However, the histogram of the absolute values of non-redundant residual-correlations (Fig\@ref(fig:Residuals) showed `r apa(sumR,2, T)`% correlations greater than the absolute value of .05, indicating a possible under-factoring. [@desjardinsHandbookEducationalMeasurement2018a]. Subsequently, we fitted a six-factor solution. However, a factor emerged with only one salient variable loading in the six-factor solution, thus disqualifying the six-factor solution.
